Verifying Demonstrations

### 2018-11-09 paper/verifiability-properties.tex
Fixes Douglas' comments in verifiability-properties

We note that, in general terms, protesting is very similar to petitions, which in turn are similar to voting.
Indeed, all three situations correspond to cases in which many individuals express their opinion.
These opinions can be sensitive (\eg be a cause for discrimination or persecution), hence we desire to have similar properties of verification and privacy for verifying a protest as there are for voting.
(We discuss privacy in \cref{privacy-properties}.)

We draw inspiration from the three general desirable properties for 
verifiability, as summarized by 
\textcite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{description}
  \item[Eligibility:] anyone can verify that each cast vote is legitimate.
  \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
  \item[Individual verifiability:] each voter can verify that his vote is included in the result.
\end{description}
In our context, votes are translated into \emph{participation proofs}.
Universal and individual verifiability remain the same, in the sense that 
anyone can verify the participation count by counting the proofs.
The eligibility requirement is slightly different as for protests it must include temporal and spatial eligibility (\ie each participation proof satisfies some temporal and spatial relation to the protest).
In essence, the proof must bind the person to the time and location of the protest.

>>>>

We note that, in general terms, protesting is very similar to petitions, which in turn are similar to voting.
Indeed, all three situations correspond to situations in which many individuals express their opinion.
These opinions can be sensitive (\eg be a cause for discrimination or persecution), hence we desire to have similar properties of verification and privacy for verifying a protest as there are for voting.
(We discuss privacy in \cref{privacy-properties}.)

We draw inspiration from the three traditionally desired properties for 
verifiability for voting:
% XXX find a new ref for voting verifiability properties
\begin{description}
  \item[Eligibility:] anyone can verify that each cast vote is legitimate.
  \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
    % Douglas: technically this is Sako-Kilian
  \item[Individual verifiability:] each voter can verify that his vote is included in the result.
    % Douglas: this is much earlier than Sako-Kilian, in essence Fiat-Shamir.
\end{description}
In our context, votes are translated into \emph{participation proofs}.
Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs.
The eligibility requirement is slightly different as for protests it must 
include temporal\footnote{%
  Elections also has some temporal aspects, \eg one cannot vote at any time and 
  a vote in one election should not be reusable in the next election.
  However, the temporal relation for a protest is not as strictly defined as 
  for elections, a protest can start at any time and last for an arbitrary 
  period of time.
} and spatial eligibility (\ie each participation proof satisfies some temporal 
and spatial relation to the protest).
In essence, the proof must bind the person to the time and location of the protest.
